Pretty darn good control: when are approximate solutions better than approximate models

### 2023-07-03 manuscript/manuscript.Rmd
mini

```{r}
#| label: conceptual-v2
#| echo: FALSE
#| message: FALSE
#| fig.align: 'center'
#| fig.cap:  'An experimental-design type of visualization of the management scenarios considered in this paper. 
#| On the x-axis are four different fishery management problems (Table 1).
#| We represent the Model 4’s non-stationarity with a clock next to the X variable, and we intend to use it as an example of a possible simplified model for the effects of climate change.
#| On the y-axis we have different management strategies with which one may control each of the models. 
#| On the bottom we have the constant escapement strategy (CEsc), based on calling off all fishing below a certain threshold population value.
#| Above that is the constant mortality strategy (CMort), where one optimizes over constant fishing effort strategies.
#| Finally, on top we have DRL-based strategies where policies are in general functions of the full state of the system, and they are parametrized by a neural network.
#| The specific DRL-based strategy is referred to as PPO+GP in the main text, due to the algorithm used to produce the policy.
#| The results plotted are the average reward obtained by the strategy over 100 episodes, and the fraction of those episodes which do not end with a near-extinction event (denoted 'Perc' for 'Percentage').
#| We have normalized to the highest reward in each column in order to enhance the comparison between strategies.
#| For illustrative purposes we have color-coded the results using a two-dimensional color legend displayed on the bottom left.'
#| out.width: '6.5in' 
#| fig.pos: 'H'

>>>>

```{r}
#| label: conceptual-v2
#| echo: FALSE
#| message: FALSE
#| fig.align: 'center'
#| fig.cap:  'An experimental-design type of visualization of the management scenarios considered in this paper. 
#| On the x-axis are four different fishery management problems (Table 1).
#| We represent the Model 4’s non-stationarity with a clock next to the X variable, and we intend to use it as an example of a possible simplified model for the effects of climate change.
#| On the y-axis we have different management strategies with which one may control each of the models. 
#| On the bottom we have the constant escapement strategy (CEsc), based on calling off all fishing below a certain threshold population value.
#| Above that is the constant mortality strategy (CMort), where one optimizes over constant fishing effort strategies.
#| Finally, on top we have DRL-based strategies where policies are in general functions of the full state of the system, and they are parametrized by a neural network.
#| The specific DRL-based strategy is referred to as PPO+GP in the main text, due to the algorithm used to produce the policy.
#| The results plotted are the average reward obtained by the strategy over 100 episodes, and the fraction of those episodes which do not end with a near-extinction event (denoted Perc for Percentage).
#| We have normalized to the highest reward in each column in order to enhance the comparison between strategies.
#| For illustrative purposes we have color-coded the results using a two-dimensional color legend displayed on the bottom left.'
#| out.width: '6.5in' 
#| fig.pos: 'H'
